Keystoneness, centrality, and the structural controllability of ecological networks

### 2018-07-19 paper/manuscript.Rmd
Update keywords

**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species importance, control capacity

>>>>

**Keywords:** Keystone species, management interventions, mutualism, network control theory, plant population and community dynamics, species importance, control capacity, structural stability, controllability
